Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-05 ms.tex
added 320x320 results and compared to 2048x256

>>>>

\clearpage
\subsection{320 Subarray test}
We also explored the stability of a $320 \times 320$ subarray.
The subarray was placed at a strategic location on each detector to allow horizontally-displaced background aperture as shown in Figure \ref{fig:sub320AperturesAZlab06}.

Surprisingly, the subarray mode had considerably higher scatter from integration to integration than stripe mode.
They both had 1000 integrations, a 6.0 mA LED current and similar aperture widths.
The subarray mode had 10 groups versus 8 groups with the stripe mode.
The subarray was $320 \times 320$ with one amplifier output whereas the stripe mode was $2048 \times 256$ with 4 amplifier outputs.

\begin{figure*}
\gridline{
\fig{ap_labels_azlab06sub320Baseline487_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 487}\\
\fig{ap_labels_azlab06sub320Baseline488_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 488}
}
\gridline{
\fig{ap_labels_azlab06sub320Baseline489_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 489}\\
\fig{ap_labels_azlab06sub320Baseline490_NRCSUB320LED6P0MA.pdf}{0.3\textwidth}{Detector 490}
}
\caption{Source apertures (labeled ``0'') and horizontally-displaced background apertures for the AZLab 06 $320 \times 320$ subarray test.}\label{fig:sub320AperturesAZlab06}
\end{figure*}

\begin{figure*}
\gridline{
\fig{individual_azlab06_baseline3.pdf}{0.49\textwidth}{Stripe Baseline $2048 \times 256$}\\
\fig{individual_azlab06_sub320_6p0mA}{0.49\textwidth}{Subarray Baseline $320 \times 320$}
}
\caption{The time series of the AZLab 06 $320 \times 320$ subarray shows considerably higher scatter than the stripe mode.}\label{fig:sub320vsStripeBaseline2}
\end{figure*}
